---
title: "datateachr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to datateachr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(datateachr)
```

The goal of `datateachr` is to provide an easy way to access open source data for educational purposes. It contains several semi-tidied data sets obtained from multiple sources.

## Installation

You can install the development version from [GitHub](https://github.com/UBC-MDS/datateachr) with:

## Data

This package currently contains the following data sets:
  
  - `apt_buildings`: Acquired courtesy of [The City of Toronto's Open Data Portal](https://open.toronto.ca/). It currently has `r nrow(apt_buildings)` rows and `r ncol(apt_buildings)` columns.
  
  - `building_permits`: Acquired courtesy of [The City of Vancouver's Open Data Portal](https://opendata.vancouver.ca/pages/home/). It currently has `r nrow(building_permits)` rows and `r ncol(building_permits)` columns.
  
  - `cancer_sample`: Acquired courtesy of [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/index.php). It currently has `r nrow(cancer_sample)` rows and `r ncol(cancer_sample)` columns.
  
  - `flow_sample`: Acquired courtesy of [The Government of Canada's Historical Hydrometric Database](https://wateroffice.ec.gc.ca/mainmenu/historical_data_index_e.html). It currently has `r nrow(flow_sample)` rows and `r ncol(flow_sample)` columns.
  
  - `parking_meters`: Acquired courtesy of [The City of Vancouver's Open Data Portal](https://opendata.vancouver.ca/pages/home/). It currently has `r nrow(parking_meters)` rows  and `r ncol(parking_meters)` columns.
  
  - `steam_games`: Acquired courtesy of [Kaggle](https://www.kaggle.com/trolukovich/steam-games-complete-dataset). It currently has `r nrow(steam_games)` rows and `r ncol(steam_games)` columns.
  
  - `vancouver_trees`: Acquired courtesy of [The City of Vancouver's Open Data Portal](https://opendata.vancouver.ca/pages/home/). It currently has `r nrow(vancouver_trees)` rows and `r ncol(vancouver_trees)` columns.

 
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE}
library(dplyr)
library(datateachr)


vancouver_trees %>%
  filter(genus_name == "ACER") %>% 
  arrange(desc(diameter)) %>%
  head()
```


## Citation

Run this command to get information about how to cite this package.

```{r warning = FALSE}
citation("datateachr")
```
